### 2020-10-01 reports/article.tex
simplifying - no calibration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
% \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

@@

% use "section" label for sections, subsections and subsubsections with the `autoref` command
% https://tex.stackexchange.com/questions/177007/autoref-showing-subsection-and-subsubsection
\let\subsectionautorefname\sectionautorefname
\let\subsubsectionautorefname\sectionautorefname

@@

% figures
\usepackage{graphicx}

% multiple figures
\usepackage{subcaption}

@@

\begin{document}

% \defcitealias{sfso2020statistique}{SFSO}

% \title[Author guidelines for IOP Publishing journals in  \LaTeXe]{How to prepare and submit an article for publication in an IOP Publishing journal using \LaTeXe}

\author{Mart\'i Bosch$^1$}

\address{$^1$ Urban and Regional Planning Community (CEAT), \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
\ead{marti.bosch@epfl.ch}

\begin{abstract}

\end{abstract}

%
% Uncomment for keywords
%\vspace{2pc}
%\noindent{\it Keywords}: XXXXXX, YYYYYYYY, ZZZZZZZZZ
%
% Uncomment for Submitted to journal title message
%\submitto{\JPA}
%
% Uncomment if a separate title page is required
%\maketitle
% 
% For two-column output uncomment the next line and choose [10pt] rather than [12pt] in the \documentclass declaration
%\ioptwocol
%

\section{Introduction}

\section{Materials and Methods}

\subsection{Study area}

@@

The population data for the study area has been extracted from the population and households statistics (STATPOP) \cite{sfso2020statistique} provided by the Swiss Federal Statistical Office (SFSO) with the Python library swisslandstats-geopy \cite{bosch2019swisslandstats}.

% BEGIN %
% \subsection{Simulation with the InVEST urban cooling model}

% The spatial distribution of UHI is simulated with the InVEST urban cooling model (version 3.8.0) \cite{sharp2020invest}, which is based on the heat mitigation provided by shade, evapotranspiration and albedo.
% The main inputs are a LULC raster map, a reference evapotranspiration raster and a biophysical table containing model information of each LULC class of the map. Each row of the biophysical table represents a LULC class, and features the following columns:

% \begin{itemize}
% \item \texttt{lucode} the LULC class code as represented in the LULC raster map
% \item \texttt{Shade} a value between 0 and 1 representing the proportion of tree cover in such LULC class
% \item \texttt{Kc} the evapotranspiration coefficient
% \item \texttt{Albedo} a value between 0 and 1 representing the proportion of solar radiation directly reflected by the LULC class
% \item \texttt{Green\_area} whether the LULC class should be considered a green area
% \item \texttt{Building\_intensity} a value between 0 and 1 representing the ratio between floor area and land area
% \end{itemize}

% In order to simulate the spatial distribution of $T_{air}$, the model requires two additional inputs. The first is the rural reference temperature $T_{ref}$, where the UHI effect is not observed, e.g., in the rural surroundings of the city. The second is the magnitude of the urban heat island effect $UHI_{max}$, namely the difference between the rural refrence temperature and the maximum $T_{air}$ observed in the city center.

% \subsubsection{Model description}

% The data inputs described above are then used to compute the cooling capacity index, which is based on the physical mechanisms that contribute to cooling urban temperatures. More precisely, the cooling capacity index used in InVEST urban cooling model builds upon the indices proposed by Zardo et al. \cite{zardo2017estimating}, which are based on shading and evapotranspiration, and extends them by adding a factor to account for the albedo.
% For each pixel $i$ of the LULC raster map, the cooling capacity index is computed as in:

% \begin{equation}
%   \label{eq:cooling-capacity}
%   CC_i = w_{S} \cdot \textrm{S}_i + w_{AL} \cdot \textrm{AL}_i + w_{ET} \cdot \textrm{ETI}_i
% \end{equation}

% where $S_i$, $AL_i$ and $ETI_i$ respectively represent the tree shading, albedo and evapotranspiration values of pixel $i$ as defined in the biophysical table, and $w_{S}$, $w_{AL}$ and $w_{ET}$ represent the weights attributed to each component respectively.
% The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the LULC class of the pixel $i$ (see \autoref{tab:biophysical-table}).
% The tree shading coefficient corresponds to the average proportion of tree cover in all the 10~m pixels of each LULC class, which has been computed by coupling the 1~m binary tree canopy mask with the rasterized 10~m LULC map.
% The albedo coefficients are based on the local climate zone classification by Steward and Oke \cite{stewart2012local}.

% % \subsubsection*{Evapotranspiration}

% The evapotranspiration index $ETI$ is computed as a normalized value of the potential evapotranspiration as in:

% \begin{equation}
%   \label{eq:evapotranspiration-index}
%   ETI = \frac{K_c \cdot ET_{ref}}{ET_{max}}
% \end{equation}

% where $K_c$ is the evapotranspiration coefficient, $ET_{ref}$ is the reference evapotranspiration raster for the period and area of interest and $ET_{max}$ is the maximum evapotranspiration value observed in the area of interest.

% % \paragraph{Adjustment of the crop coefficient}

% In line with the studies of Nistor et al. \cite{nistor2015compute,nistor2016climate,nistor2016mapping}, the evapotranspiration coefficients are attributed to each LULC class by distinguishing four cases, namely the crop coefficient for single crops for vegetation LULC classes, the water evaporation coefficient for surface water, the rock and soil evaporation coefficient for bare soils and rocks, and evaporation coefficients for artificial LULC classes (e.g., urban areas).
% The evapotranspiration coefficients attributed to the LULC classes of the Swiss cadastral survey are listed in \autoref{tab:biophysical-table}.

% % \paragraph{Computation of the evapotranspiration}

% Following the recommendations of Allen et al. \cite{allen1998crop}, the daily evapotranspiration $ET_{ref}$ (in $mm/day$) has been estimated for each pixel using the Hargreaves equation \cite{hargreaves1985reference} as in:

% \begin{equation}
%   \label{eq:ref-evapotranspiration}
%   ET_{ref} = 0.0023 \cdot (T_{avg} + 17.8) \cdot (T_{max} - T_{min})^{0.5} \cdot R_a
% \end{equation}

% where $T_{avg}$, $T_{max}$ and $T_{min}$ respectively correspond to the average, maximum and minimum $T_{air}$ (in \degree C) of each day and $R_a$ is the extraterrestrial radiation (in $mm/day$), which is in turn estimated for the latitude of Lausanne (i.e., 46.519833\degree) for each date following the methods of Allen et al. \cite[Equation 21]{allen1998crop}.
% The temperature values of each day have been extracted from the inventory of gridded datasets provided by the Federal Office of Meteorology and Climatology (MeteoSwiss), which feature the minimum, average and maximum daily $T_{air}$ for the extent of the whole country at a resolution of 1~km. Such a dataset is obtained by interpolating 100 $T_{air}$ stations accross Switzerland (including the MeteoSwiss Pully station) based on non-linear thermal profiles of major basins and non-Euclidean distance weighting that accounts for terrain effects \cite{frei2014interpolation}.

% In order to account for the cooling effect of large green spaces, the computed cooling capacity index of pixels that are part of large green areas ($>$ 2~ha) is adjusted as in:

% \begin{equation}
%   \label{eq:cooling-capacity-green}
%   CC_i^{green} = \sum_{j \in \Omega_i} g_i \cdot CC_j \cdot e^{-\frac{d(i, j)}{d_{cool}}}
% \end{equation}

% where $g_i$ is 1 when the pixel $i$ is a green area and 0 otherwise (as defined in the biophyisical table), $d(i, j)$ is the distance between pixels $i$ and $j$, $d_{cool}$ is a parameter that defines the distance over which a green space has a cooling effect, and $\Omega_i$ is the set of pixels whose distance to $i$ is lower than $d_{cool}$.

% Then, a heat mitigation index is computed as:

% % $\; if \;\; i \; \textrm{is part of a large green area} \;\; or \;\; CC_i > CC_i^{green}$
% % $\; otherwise$
% \begin{equation}
%   \label{eq:heat-mitigation index}
%   HM_i=\cases{
%     CC_i & if \; i $\in$ \textrm{large green area} \;\; or \;\; $CC_i > CC_i^{green}$ \\
%     CC_i^{green} & otherwise \\
%   }
% \end{equation}

% which is employed to compute the $T_i$ for each pixel $i$ of the study area as in:

% \begin{equation}
%   \label{eq:tair-nomix}
%   T_i^{no \, mix} = T_{ref} + (1 - HM_i) \cdot UHI_{max}
% \end{equation}

% where $T_{ref}$ and $UHI_{max}$ are the rural reference temperature and the magnitude of the UHI effect respectively, as described above.
% Finally, the $T_{air}$ values of each pixel $T_i^{no \, mix}$ are spatially averaged using a Gaussian function with a kernel radius $r$ defined by the user.

% END %

\subsection{Simulation with the InVEST urban cooling model}

@@

where $S_i$, $AL_i$ and $ETI_i$ respectively represent the tree shading, albedo and evapotranspiration values of pixel $i$ as defined in the biophysical table, and $w_{S}$, $w_{AL}$ and $w_{ET}$ represent the weights attributed to each component respectively.
The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the LULC class of the pixel $i$ (see \autoref{tab:biophysical-table}), whereas the reference evapotranspiration $ETI_i$ pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum $T_{air}$ values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation} (see Bosch et al. \cite{bosch2020spatially} for more details on the estimation of $ETI_i$).

@@

% $\; if \;\; i \; \textrm{is part of a large green area} \;\; or \;\; CC_i > CC_i^{green}$
% $\; otherwise$
\begin{equation}
  \label{eq:heat-mitigation index}
  HM_i=\cases{
    CC_i & if \; i $\in$ \textrm{large green area} \;\; or \;\; $CC_i > CC_i^{green}$ \\
    CC_i^{green} & otherwise \\
  }
\end{equation}

@@

Following the calibration of the model to the same study area by Bosch et al. \cite{bosch2020spatially}, the values of the cooling capacity weights have been set to $w_{S} = 0.59$, $w_{AL} = 0.24$ and $w_{ET} = 0.17$, the distance over which green spaces have a cooling effect $d_{cool}$ and the air mixing radius $r$ have been set

\subsubsection{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

@@

In order to adapt the biophysical table to the reclassified LULC classes, the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \ref{sec:biophysical-table}).

@@

\subsection{Generation of greening scenarios}

% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
% TODO: limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100~\%
% TODO: randomized

% with two main objectives. The first objective is to use the scenarios to explore the relationships between spatial patterns in both composition and configuration of trees and the distribution of air temperature simulated with the urban cooling model. The second objective is to inform policy-making.
% In order to explore the relationships between spatial pattern of the tree canopy in each scenario and its respective distribution of air temperature simulated with the urban cooling model.
In order to quantify spatial pattern of the tree canopy of each scenario, a set of spatial metrics from landscape ecology \cite{o1988indices,mcgarigal2012fragstats} will be computed for the pixels whose post-refinement LULC class has a high tree canopy cover.  % over a certain threshold.
% deux pixels adjacents forment une canopée continue. Pour arriver à une telle conclusion, une typologie d’arbre est fixée. Sur recommandations de la Direction des ressources et du patrimoine naturel du canton de Vaud (DGE), une canopée coninue serait constituer d’arbres disposant d’une couronne sphérique de 5m de rayon, espacés chacun de 10m. Au vue de la dimension des pixels issus de la couche reclassifée (100 m 2 ), une telle typologie d’arbre correspondrait à une canopée de 75 m 2 , soit un degré de recouvrement de 75%
Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75~\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.
Based on related studies, four spatial metrics have been chosen to quantify both the composition and oconfiguration of the tree canopy, which are listed in \autoref{tab:selected-metrics}. The proportion of landscape (PLAND) of pixels with high tree canopy cover serves to quantify the composition aspects, while the configuration is quantified by means of the mean patch size (MPS), edge density (ED) and the mean shape index (MSI) of patches of high tree canopy cover. The four metrics have been computed with the Python library PyLandStats \cite{bosch2019pylandstats}.

\begin{table}[!h]
  % \begin{adjustwidth}{-.4\textwidth}{0cm} % Comment out/remove adjustwidth environment if table fits in text column.
  \footnotesize % Font size can be changed to match table content. Recommend 10 pt.
  \caption{\label{tab:selected-metrics}Selected landscape metrics. A more thorough description can be found in the documentation of the software FRAGSTATS v4 \cite{mcgarigal2012fragstats}}
  \renewcommand{\arraystretch}{1.5} % vertical spacing
  \begin{center}
  \begin{tabular}{p{.13\textwidth} p{.34\textwidth} p{.53\textwidth}} 
    \toprule
    \textbf{Category} & \textbf{Metric name} & \textbf{Description} \\
    \midrule
    Composition & Percentage of landscape (PLAND) & Percentage of landscape, in terms of area, occupied by pixels with high tree canopy cover \\
    Configuration & Mean patch area (AREA\_MN) & Average size (in hectares) of the patches formed by pixels with high tree canopy cover \\
    & Mean shape index (SHAPE\_MN) & Average shape index of the patches formed by pixels with high tree canopy cover \\
    & Edge density (ED) & Sum of the lengths of all edge segments between pixels with high tree canopy cover an other pixels, per area unit (in m/hectare) \\    
    \bottomrule  
  \end{tabular}
  \end{center}
  % \end{adjustwidth}
\end{table}

\section{Results}

@@

\subsection{LULC change}

The relationship between the number of pixels by LULC class changed and the proportion of pixels changed to its corresponding LULC class with high tree canopy cover is shown in \autoref{fig:greening-lulc-change}.

\begin{figure}
  \centering
  \includegraphics[width=.6\textwidth]{figures/greening-lulc-change} 
  \caption{\label{fig:greening-lulc-change} Number of pixels by LULC class changed for proportions of pixels changed to its LULC code with high tree canopy cover of  0.25, 0.5, 0.75 and 1. The lines represent the 95\% confidence intervals.}
\end{figure}

The confidence intervals are small for all the proportions of pixels changed (and of course, inexistent when changing all the possible pixels), which suggests that .

\subsection{Effect of the proportion of tree cover}

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in,marginparwidth=2in]{geometry}

% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8]{inputenc}

% clean citations
\usepackage{cite}

@@

% line numbers
\usepackage[right]{lineno}

% improves typesetting in LaTeX
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% text layout - change as needed
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Remove % for double line spacing
%\usepackage{setspace} 
%\doublespacing

% use adjustwidth environment to exceed text width (see examples in text)
\usepackage{changepage}

% adjust caption style
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,singlelinecheck=off]{caption}

% remove brackets from references
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% headrule, footrule and page numbers
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}

% use \textcolor{color}{text} for colored text (e.g. highlight to-do areas)
\usepackage{color}

% define custom colors (this one is for figure captions)
\definecolor{Gray}{gray}{.25}

% this is required to include graphics
\usepackage{graphicx}

% use if you want to put caption to the side of the figure - see example in text
\usepackage{sidecap}

% use for have text wrap around figures
\usepackage{wrapfig}
\usepackage[pscoord]{eso-pic}
\usepackage[fulladjust]{marginnote}
\reversemarginpar

@@

% math utils
\usepackage{amsmath}

@@

% % citation aliases
% \usepackage{natbib}
% % https://tex.stackexchange.com/questions/323868/setting-two-different-aliases-name-2016-name-2016-with-defcitealias
% \newcommand{\mycitet}[1]{\citetalias{#1} (\citeyear{#1})}
% \newcommand{\mycitep}[1]{(\citetalias{#1} \citeyear{#1})}

% force floats in sections
\usepackage{float}

% \usepackage{caption}

% document begins here
\begin{document}
\vspace*{0.35in}

% \defcitealias{arezh2018bodenbedeckung}{ARE}
% \defcitealias{asitvd2018structure}{ASIT VD}
% \defcitealias{bve2019mopube}{BVE}

% title goes here:
\begin{flushleft}
{\Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
\textbf\newline{}
}
\newline
% authors go here:
\\
Mart\'i Bosch\textsuperscript{*},
% Maxence Locatelli,
% J\'er\^ome Chenal
\\
\bigskip
Urban and Regional Planning Community (CEAT), \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland
\\ 
\bigskip
* Corresponding author: marti.bosch@epfl.ch

\end{flushleft}

\section*{Abstract}

% now start line numbers
\linenumbers

% the * after section prevents numbering
\section*{Introduction}

% Distinction: three types of UHI: urban boundary layer, urban canopy layer \cite{oke1976distinction}

% ``We know that simply increasing the percent cover of greenspace leads to a reduction of temperatures; this relationship is very consistent. What is less known, however, is the effects of the spatial configuration of that greenspace on urban temperatures'' \cite[page 2]{zhou2017effects}
% The complexity of such relationship might only be understood by means of a spatially-explicit analysis. Several studies have addressed the effects of landscape composition and pattern on land surface temperature (LST), e.g., derived from satellite imagery, by means of statistical approaches (e.g., ordinary regressions or spatial autoregressions). 
% non-linear interplay between landscape patterns and ecological processes \cite{du2016quantifying}
% Note that while most studies that use single-level statistical models suggest that landscape composition has greater influence on LST than landscape configuration, the multi-level models used by Du et al. \cite{du2016quantifying} suggest the opposite. Why? (i) group-based configuration metrics consider the autocorrelations of the configuration metrics, and (ii) the aggregation effects of the groups and the individual effects of the pixels are distinguished by the multi-level models.
% Note however further limitations of statistical approaches in general:
% ``Our results from the comparison of the two cities indicated that the spatial configuration of trees may have different effects on LST in cities with different climatic conditions'' \cite[page 6]{zhou2017effects}
% This might be due to the fact that the relative contributions of the two main cooling mechanisms associated to urban trees, namely shading and evapotranspiration, can be related to the different climatic conditions of the modelled cities \cite{zhou2017effects}.
% Nevertheless, the statistical approaches employed in such studies (e.g., ordinary regressions or spatial autoregressions with LST as response and landscape metrics as explanatory variables) do not explicitly reflect the physical mechanisms beyond the urban heat island phenomena.

% MAYBE: greening \cite{jabareen2006sustainable}

Urbanization is nowadays a global phenomenon that is increasingly concentrating the world's population in urban areas, which are expected to grow in both the number of dwellers and spatial extent \cite{seto2011meta, angel2012atlas, unitednations2018world}.
As a major force of landscape change, urbanization is characterized by the conversion of natural to artificial surfaces, which alters the energy and water exchanges as well as the movement of air. Such changes often result in the urban heat island (UHI) effect, a phenomena by which urban temperatures are warmer than its rural surroundings \cite{oke1982energetic}.

% As urban areas grow and global temperatures increase, heat waves are expected to become more intense and frequent ant the UHI effect
As urban areas grow and global temperatures rise, the UHI effect is expected to become more intense \cite{meehl2004more,huang2019projecting}, which makes urban heat mitigation a major priority for urban planning and policy-making.
% Green infrastructure
% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Overall decrease of urban green space in European cities due to infill development \cite{haaland2015challenges}.
% TODO: challanges with densification, trade-offs in the provision of ecosystem services
% TODO: need for methods to quantify
Nevertheless, the impact of the abundance and spatial configuration of the urban tree canopy on air temperature shows a complex spatial behaviour that remains
Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.

The present work introduces a novel approach to spatially evaluate the heat mitigation potential that could be achieved by increasing the urban tree canopy cover in the urban agglomeration of Lausanne, Switzerland. The proposed method consists of three major parts.
% 1. Couple the cadastral LULC map with a high-resolution tree canopy map to detect locations where the tree canopy cover can be increased
% 2. Generate a variety of synthetic scenarios by increasing the tree canopy cover, which can mimic urban greening strategies. % in different spatial configurations
% 3. 
First, the cadastral LULC map is coupled with a high-resolution tree canopy map to detect candidate pixels where the tree canopy cover can be increased.
Secondly, a set of synthetic scenarios is generated by increasing the tree canopy cover in the candidate pixels.
% is applied with the LULC map that corresponds to 
% Finally, the synthetic LULC map of each scenario is fed to the InVEST urban cooling model in order to estimate the air temperature of
Finally, the spatial distribution of air temperature of each scenario is estimated by applying the InVEST urban cooling model to the corresponding synthetic LULC map.

\section*{Materials and Methods}

\subsection*{Study area}

@@

In order to evaluate the human thermal comfort, the population data for the study area has been extracted from the population and households statistics (STATPOP) \cite{sfso2020statistique} provided by the Swiss Federal Statistical Office (SFSO) with the Python library swisslandstats-geopy \cite{bosch2019swisslandstats}.

\subsection*{Simulation with the InVEST urban cooling model}

@@

where $S_i$, $AL_i$ and $ETI_i$ respectively represent the tree shading, albedo and evapotranspiration values of pixel $i$ as defined in the biophysical table, and $w_{S}$, $w_{AL}$ and $w_{ET}$ represent the weights attributed to each component respectively.
The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the LULC class of the pixel $i$ (see \autoref{tab:biophysical-table}), whereas the reference evapotranspiration $ETI_i$ pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum $T_{air}$ values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation} (see Bosch et al. \cite{bosch2020spatially} for more details on the estimation of $ETI_i$).
% The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the post-refinement LULC class of the pixel $i$, e.g., the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \ref{sec:biophysical-table}). On the other hand, the reference evapotranspiration $ETI_i$ pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum $T_{air}$ values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation} (see Bosch et al. \cite{bosch2020spatially} for more details on the estimation of $ETI_i$).

@@

% $\; if \;\; i \; \textrm{is part of a large green area} \;\; or \;\; CC_i > CC_i^{green}$
% $\; otherwise$
\begin{equation}
  \label{eq:heat-mitigation index}
  HM_i=\begin{cases}
    CC_i & if \; i \in \textrm{large green area} \;\; or \;\; CC_i > CC_i^{green} \\
    CC_i^{green} & otherwise \\
  \end{cases}
\end{equation}

@@

Following the calibration of the model to the same study area by Bosch et al. \cite{bosch2020spatially}, the values of the cooling capacity weights have been set to $w_{S} = 0.59$, $w_{AL} = 0.24$ and $w_{ET} = 0.17$, the distance over which green spaces have a cooling effect $d_{cool}$ and the air mixing radius $r$ have been set to 89.21 and 236.02~m respectively.
The $T_{ref}$ and $UHI_{max}$ values have been set based on the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ has been set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ has been set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

\subsection*{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

@@

In order to adapt the biophysical table of the InVEST urban cooling model to the reclassified LULC classes, the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \autoref{tab:biophysical-table}).

@@

\subsection*{Generation of urban greening scenarios}

% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
% Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
% More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
Departing from the refined LULC map, a set of urban greening scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100~\%
In order to ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, the transformed pixels . First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown. Secondly, pixels of the ``road, path'' class might only be transformed when they are next to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).

% with two main objectives. The first objective is to use the scenarios to explore the relationships between spatial patterns in both composition and configuration of trees and the distribution of air temperature simulated with the urban cooling model. The second objective is to inform policy-making.
% In order to explore the relationships between spatial pattern of the tree canopy in each scenario and its respective distribution of air temperature simulated with the urban cooling model.
% In order to quantify spatial pattern of the tree canopy of each scenario, a set of spatial metrics from landscape ecology \cite{o1988indices,mcgarigal2012fragstats} are computed for the pixels whose post-refinement LULC class has a high tree canopy cover.  % over a certain threshold.
For each scenario, the spatial pattern of the tree canopy is quantified by means of a set of spatial metrics from landscape ecology \cite{o1988indices,mcgarigal2012fragstats}, which are computed for the pixels whose post-refinement LULC class has a tree canopy cover over 75\% \footnote{Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75~\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.}.
Based on other studies that explore the relationship between the spatial of tree canopy and UHIs, four spatial metrics have been chosen to quantify both the composition and oconfiguration of the tree canopy, which are listed in \autoref{tab:selected-metrics}. The proportion of landscape (PLAND) of pixels with high tree canopy cover serves to quantify the composition aspects, while the configuration is quantified by means of the mean patch size (MPS), edge density (ED) and the mean shape index (MSI) of patches of high tree canopy cover. The four metrics have been computed with the Python library PyLandStats \cite{bosch2019pylandstats}.

\begin{table}[!h]
  \begin{adjustwidth}{-.4\textwidth}{0cm} % Comment out/remove adjustwidth environment if table fits in text column.
    % \footnotesize % Font size can be changed to match table content. Recommend 10 pt.
    \caption{\label{tab:selected-metrics}Selected landscape metrics. A more thorough description can be found in the documentation of the software FRAGSTATS v4 \cite{mcgarigal2012fragstats}}
    \renewcommand{\arraystretch}{1.5} % vertical spacing
    \begin{center}
      \begin{tabular}{p{.15\textwidth} p{.4\textwidth} p{.76\textwidth}} 
        \toprule
        \textbf{Category} & \textbf{Metric name} & \textbf{Description} \\
        \midrule
        Composition & Percentage of landscape (PLAND) & Percentage of landscape, in terms of area, occupied by pixels with high tree canopy cover \\
        Configuration & Mean patch area (AREA\_MN) & Average size (in hectares) of the patches formed by pixels with high tree canopy cover \\
        & Mean shape index (SHAPE\_MN) & Average shape index of the patches formed by pixels with high tree canopy cover \\
        & Edge density (ED) & Sum of the lengths of all edge segments between pixels with high tree canopy cover an other pixels, per area unit (in m/hectare) \\    
        \bottomrule  
      \end{tabular}
    \end{center}
  \end{adjustwidth}
\end{table}

\subsubsection*{Simulation of urban greening by randomly increasing the proportion of tree cover}
With the aim of evaluating the effect of the proportion of tree cover on air temperature, a set of scenarios is generated by transforming a 25, 50, 75 and 100\% of the pixels where the tree canopy cover can be increased.
For each of the aforementioned percentages, 10 scenarios will be generated by randomly sampling from the candidate pixels until the desired proportion of changed pixels is matched. Therefore, the temperature maps for each of the percentage of changed pixels will be computed by averaging the 10 respective simulated runs.

\subsubsection*{Simulation of distinct urban greening approaches by clustering and scattering trees}

% To expore the relationship between
In order to obtain a greater variety of spatial patterns of tree canopy cover and further explore the relationship between the spatial configuration of tree canopy and UHIs, two additional sets of scenarios will be generated.
% Like the first set of scenarios described above, these two additional sets are also produced by transforming a 25, 50, 75 and 100\% of the pixels where the tree canopy can be increased.
% Nevertheless, in these two sets the transformed pixels are not randomly sampled but selected according to the number of pixels with high tree canopy cover (i.e., > 75\%) found in their Moore neighborhood. Therefore,
In these sets of scenarios, the transformed pixels are not randomly sampled but selected according to the number of pixels with high tree canopy cover (i.e., greater than 75\%) found in their Moore neighborhood.
Therefore, the first set of scenarios pixels with higher number of high tree canopy cover neighbors are transformed first, which intends to spatially cluster pixels of high tree canopy cover. Conversely, the second set of scenarios intends to spatially scatter pixels of high tree canopy cover by giving precedence to pixels with lower number of high tree canopy neighbors.
To explore the difference between the two approaches with more detail, these two sets of scenarios will be produced by transforming a 12.5, 25, 37.5, 50, 62.5, 75, 87.5 and 100\% of the pixels where the tree canopy can be increased.
Like the previous set of scenarios, the temperature maps will be computed by averaging the results of 10 simulation funs for each configuration, i.e., combination of proportion of changed pixels and spatial approach of either clustering or scattering the transformed pixels.

\section*{Results}

@@

\subsection*{LULC change}
